Avoidance in permutations

### 2014-11-05 project2/paper/paper.tex
Cleaned up t_n(312) = t_n(321) proof

We now construct a bijective mapping between all permutations in $T_n$ that avoid $312$ and all permutations in $T_n$ that avoid $321$.

@@

\textbf{May want to skip the transformation stuff, and directly talk about the bijection being established.}

@@

What remains to be proven is that the order of swapping operations in the chain of transformations does not matter -- that is, any valid transformation chain starting with some permutation $\pi \in T_n$ that avoids $312$, will always produce the same permutation $\pi' \in T_n$ that avoids $321$. Note that since we're only swapping even elements, the odd elements are in exactly the same position in both $\pi$ and $\pi'$. In addition, for every element $i \in \pi$, all even numbers in $\pi$ to the right of $i$ and less than $i$ must be in decreasing order; in $\pi'$, for every element $i \in \pi'$, all even numbers in $\pi'$ to the right of $i$ and less than $i$ must be in increasing order.

>>>>

Before proving that there exists a bijective mapping between all permutations in $T_n$ that avoid $312$ (call this set $A$) and all permutations in $T_n$ that avoid $321$ (call this set $B$), we establish a chain of transformation moves that can be used to transform an element $a \in A$ to an element $b \in B$.

@@

@@

We now prove that there exists a bijection between the sets $A$ and $B$.

Let $a$ be an arbitrary permutation in $A$. Clearly, by the definition of $A$, $a$ must avoid $312$. Now, we claim that for every element $i$ in the permutation $a$, all even numbers in $a$ to the right of $i$ and less than $i$ must be in decreasing order; if this were not the case, then we would have a subsequence in the relative ordering $312$, which would be a contradiction. It is easy to see that we can make a corresponding claim about permutation $b$, that is for every element $i$ in the permutation $a$, all even numbers in $a$ to the right of $i$ and less than $i$ must be in increasing order.

The above two claims shows there's actually an easy way to transform an arbitrary permutation $a \in A$ to a $b \in B$, and similarly, to transform an arbitrary permutation $b \in B$ to a $a \in A$ -- to obtain a permutation in $B$ from a permutation $a \in A$, for every element $i$ in the permutation $a$, all even elements in $a$ to the right of $i$ less than $i$ should be reversed (that is reordered to in increasing order); similarly to obtain a permutation in $A$ from a permutation $b \in B$, for every element $i$ in the permutation $b$, all even elements in $b$ to the right of $i$, less than $i$ should be reversed (that is reordered to in decreasing order). Since the mapping from $A$ to $B$ is clearly reversible, and hence invertible, we conclude that the mapping we just established between $A$ and $B$ is bijective.
